{\it Proposal:}\\ Determining the efficacy of pulsed microwave-acoustic viral envelope disruption in COVID-19 treatment

### 2020-08-18 documents/clinical_protocol.tex
d
State

@@

{\Large \textbf{Advantages over existing techniques}}

@@

@@

>>>>

Minister of Health
Patricia Hajdu

@@

@@

The spike proteins, essential to the virus's infectivity, are

@@

\cite{neuroinvasive2020}

On the other hand, increasing evidence
shows that CoVs may first invade peripheral nerve terminals, and
then gain access to the CNS via a synapse‐connected route.

to, er, head them off at the head.

alveolar damage

https://www.nature.com/articles/s41379-020-0595-z

Inclusion criteria:

dyspnea

Patients where disease progression indicates that hypoxic respiratory failure is likely to occur.

Dyspnea
Oxygen saturation
CT: lung opacities

Without metal piercings or

Non-thermal nerve stimulation leading to temporary paralysis has been reported.

Since the genitals are not involved in the infection; and they will not receive a dose above background.\cite{Organ2004}.

(2) The application must contain sufficient information and material to enable the Minister to determine whether to issue the authorization and must include the following:

the name and contact information of the applicant 
the name and class of the device;
a description of the device and of the materials used in its manufacture and packaging;
a description of the features of the device that permit it to be used for the medical conditions, purposes and uses for which it is manufactured, sold or represented, including its performance specifications if those specifications are necessary for proper use;
the identifier of the device, including the identifier of any medical device that is part of a system, test kit, medical device group, medical device family or medical device group family;
the name and contact information of the manufacturer as they appear on the device label;
the address where the device is manufactured, if the address is different from the one provided in the contact information under paragraph (f);
the diagnosis, treatment, mitigation or prevention for which the device is required;
a list of the countries other than Canada where the device has been sold, the total number of units sold in those countries and a summary of any reported problems with the device and of any recalls of the device in those countries;
the known information in relation to the quality, safety and effectiveness of the device;
the directions for use, unless directions are not required for the device to be used safely and effectively;
an attestation by the applicant that documented procedures are in place in respect of distribution records, complaint handling, incident reporting and recalls;
a copy of the label of the device;
the name of the qualified investigator and their qualifications, including their training and experience;
the name and contact information of the institution at which the clinical trial is proposed to be conducted;
the protocol of the proposed clinical trial, including the number of clinical trial subjects, the number of units of the device proposed to be used for the clinical trial, the hypothesis for and objective of the clinical trial, the period of time during which the clinical trial will be conducted and a copy of the informed consent form;
a written undertaking from the qualified investigator to:
conduct the clinical trial in accordance with the protocol provided by the applicant,
inform each clinical trial subject of any risks and benefits associated with the use of the device and obtain the subject's informed consent for its use, and
not permit the device to be used by any other person except under the direction of the qualified investigator; and
in the case of a Class III or IV device, for each clinical trial site, the name and contact information of the research ethics board that approved the protocol and informed consent form referred to in paragraph (p), if known at the time of submitting the application.
Class II devices
(3) Despite subsection (2), if the application for the authorization is in respect of a Class II COVID-19 medical device, the information and material set out in paragraphs (2)‍(c), (h) to (j), (n) and (q) may be omitted from the application.
